STAT 450 Project: Real Estate

### 2020-03-30 src/2nd_draft.Rmd
1. replaced MSE with MSPE. 2. introduction of Lasso and Ridge updated

 - **Goodness of fit** is defined as the extent to which the sample data are consistent with the model, which examines how well the model explains the data. MSE (Mean Squared Error) is a measure of goodness of fit and a smaller MSE indicates better goodness of fit.

 - **Prediction power** measures how well models can predict future values. Mean squared prediction power was used to compare the prediction performance across all of our fitted linear predictive models. Prior to examine the prediction power, the data set was divided into training data - used to build our models, and testing data - used to evaluate the prediction power of our models. MSPE (Mean Squared Predction Error) on testing set is used to measure the prediction power in this study.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have a different objective function to optimize; they take a penalty in the sum of absolute values and sum of squared absolute values of weights respectively. These models have an interesting characteristic, that is, a weight is assigned to each feature. This might be relevant to our study as the mill rate can be affected by each feature to a different extent. Also, another advantage of these models is that MSPE is more stable as the variance of MSPE is reduced. For more detials about the two models, please refer to **Reference**.

@@

boxplot(mspe1.la, 
        mspe1.ri, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge",
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80",
                "pink", 
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 1,
        main = " Figure 5: Goodness of Fit",
        ylab = expression(hat(MSE)))

@@

As for goodness of fit, *Lasso*, *Ridge*, and *OLR transformed* have similar performance; MSEs across these models were around 4.6, but *OLR transformed* performed slightly better and had a smaller spread (variance) of MSE. *OLR full* performed worse than the other three, around 5.4, and *OLR null* had the greatest MSE, around 35.

>>>>

 - **Goodness of fit** is defined as the extent to which the sample data are consistent with the model, which examines how well the model explains the data. MSPE (Mean Squared Prediction Error) on training sets is a measure of goodness of fit and a smaller MSPE indicates better goodness of fit.

 - **Prediction power** measures how well models can predict future values. Mean squared prediction power was used to compare the prediction performance across all of our fitted linear predictive models. Prior to examine the prediction power, the data set was divided into training data - used to build our models, and testing data - used to evaluate the prediction power of our models. MSPE (Mean Squared Predction Error) on testing sets is used to measure the prediction power in this study.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have a different objective function to optimize; they take a penalty in the sum of absolute values and sum of squared absolute values of weights respectively. A reason to consider Ridge Regression is that it helps deal with multicollinearity of the explanatory variables. This might be relevant to our study as some features used in this study are correlated. Lasso Regression is also included in this study because it does variable selections automatically by imposing a constraint on model parameters that causes some regression coefficients to shrink to zero.

Also, another advantage of these models is that MSPE is more stable as the variance of MSPE is reduced. For more detials about the two models, please refer to **Reference**.

@@

boxplot(mspe1.la, 
        mspe1.ri, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge",
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80",
                "pink", 
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 1,
        main = " Figure 5: Goodness of Fit",
        ylab = expression(hat(MSPE)))

@@

As for goodness of fit, *Lasso*, *Ridge*, and *OLR transformed* have similar performance; MSPEs across these models were around 4.6, but *OLR transformed* performed slightly better and had a smaller spread (variance) of MSPE. *OLR full* performed worse than the other three, around 5.4, and *OLR null* had the greatest MSPE, around 35.
